---
title: "Pattern analysis"
author: "Matthieu Gallant Canguilhem"
date: "2025-01-30"
output: html_document
editor_options:
  chunk_output_type: console
---

# Setting the working directory for all chunks
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Images/Darktable/')
setwd('~/Images/Darktable/')
```


#Uploading needed packages
```{r, include=FALSE, echo=FALSE}
library(patternize)
library(tidyverse)
library(magick)
library(jpeg)
library(tiff)
library(png)
library(imager)
library(imagefx)
library(grid)
library(rstatix)
```

#test for generating image showing landmarks
```{r}
# Load image
image_path <- "Cropped_image/FG24.087_D.jpeg"
img <- image_read(image_path)
# Convert magick image to raster for ggplot
img_raster <- as.raster(img)

# Get image dimensions
img_info <- image_info(img)
img_width <- img_info$width
img_height <- img_info$height

# Read landmarks
landmarks <- read_table2("Landmarks/FG24.087_D_landmarks.txt", col_names = c("x", "y"))
landmarks2 <- read_table2("Landmarks/FG24.087_D_landmarks2.txt", col_names = c("x", "y"))
landmarks <- rbind(landmarks, landmarks2)

# Since image origin (0,0) is top-left, flip y-axis to match ggplot's bottom-left origin
landmarks$y <- img_height - landmarks$y

# Read mask polygon points (assumes same format: no headers, just x y)
mask <- read_table2("Landmarks/mask/FG24.087_D_Lforewing.txt", col_names = c("x", "y"))
mask2 <- read_table2("Landmarks/mask/FG24.087_D_Lhindwing.txt", col_names = c("x", "y"))

# Flip y-axis to match ggplot
mask$y <- img_height - mask$y
mask2$y <- img_height - mask2$y

# Close the polygon (if it's not already closed)
mask <- rbind(mask, mask[1, ])
mask2 <- rbind(mask2, mask2[1, ])

# Build plot
img_gg <- ggplot() +
  annotation_custom(rasterGrob(img_raster, width = unit(1, "npc"), height = unit(1, "npc")),
                    xmin = 0, xmax = img_width, ymin = 0, ymax = img_height) +
  geom_path(data = mask2, aes(x = x, y = y), color = "chartreuse2", linewidth = 0.9) +
  geom_path(data = mask, aes(x = x, y = y), color = "chartreuse2", linewidth = 0.9) +
  geom_point(data = landmarks, aes(x = x, y = y), color = "firebrick3", size = 2) +
  coord_fixed(xlim = c(0, img_width), ylim = c(0, img_height), expand = FALSE) +
  theme_void()

# Display plot
print(img_gg)
ggsave(filename = "image_landmarks.png", img_gg, dpi = 300)
```


# rewriting colorChecker function
```{r, setup, include=FALSE}
colorChecker2 <- function (IDlist, prepath = NULL, outpath = NULL, extension = NULL, colorCheckerType = "X-Rite",
    fixedCorners = FALSE, patchSize = 0.6, colorCheckerXY = NULL, 
    fixedModel = NULL, resampleFactor = NULL, adjustCoords = FALSE) 
{
    prop <- 1 - patchSize
    for (n in 1:length(IDlist)) {
        print(paste("Processing sample", n, IDlist[n], sep = " "))
        if (is.null(prepath)) {
            im <- imager::load.image(paste(IDlist[n], extension, 
                sep = ""))
        }
        else {
            im <- imager::load.image(paste(prepath, "/", IDlist[n], 
                extension, sep = ""))
        }
        if (!is.null(resampleFactor)) {
            imRed <- imager::resize(im, round(width(im)/resampleFactor), 
                round(height(im)/resampleFactor))
        }
        else {
            imRed <- im
        }
        mR <- raster::as.matrix(imager::R(imRed)) * 255
        mG <- raster::as.matrix(imager::G(imRed)) * 255
        mB <- raster::as.matrix(imager::B(imRed)) * 255
        rR <- raster::raster(mR)
        rG <- raster::raster(mG)
        rB <- raster::raster(mB)
        raster::extent(rR) <- c(0, dim(imRed)[2], 0, dim(imRed)[1])
        raster::extent(rG) <- c(0, dim(imRed)[2], 0, dim(imRed)[1])
        raster::extent(rB) <- c(0, dim(imRed)[2], 0, dim(imRed)[1])
        rR <- raster::flip(raster::t(rR), "y")
        rG <- raster::flip(raster::t(rG), "y")
        rB <- raster::flip(raster::t(rB), "y")
        if (all(c(colorCheckerType == "X-Rite", is.null(fixedModel)))) {
            if (is.null(colorCheckerXY)) {
                print("Click on the outer corners of the X-Rite ColorChecker (1: ~brown, 2: ~cyan, 3: ~black, 4: ~white)")
                layout(matrix(c(1, 1), 2, 1, byrow = TRUE))
                plot(imRed, xlim = c(0, width(imRed)))
                if (fixedCorners == FALSE) {
                  xy <- locator(n = 4)
                }
                if (all(c(fixedCorners == TRUE, n == 1))) {
                  xy <- locator(n = 4)
                }
            }
            if (!is.null(colorCheckerXY)) {
                xy <- list()
                xy$x <- colorCheckerXY[[n]][, 1]
                xy$y <- colorCheckerXY[[n]][, 2]
            }
            print("Matching ColorCecker patches...")
            if (is.null(colorCheckerXY)) {
                polygon(xy$x, xy$y, border = "green")
            }
            else {
                plot(imRed, xlim = c(0, width(imRed)))
                polygon(xy$x, xy$y, border = "green")
            }
            xyDF <- as.data.frame(xy)
            line1 <- xyDF[1:2, ]
            line2 <- xyDF[2:3, ]
            line3 <- xyDF[3:4, ]
            line4 <- xyDF[c(4, 1), ]
            xdiff <- (line1$x[2] - line1$x[1])/6
            ydiff <- (line1$y[2] - line1$y[1])/6
            xmin <- line1$x[1]
            ymin <- line1$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2, (xmin + xdiff * 5 + xmin + xdiff * 
                6)/2), y = c((ymin + ymin + ydiff)/2, (ymin + 
                ydiff + ymin + ydiff * 2)/2, (ymin + ydiff * 
                2 + ymin + ydiff * 3)/2, (ymin + ydiff * 3 + 
                ymin + ydiff * 4)/2, (ymin + ydiff * 4 + ymin + 
                ydiff * 5)/2, (ymin + ydiff * 5 + ymin + ydiff * 
                6)/2))
            xySubDF_1A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop, xmin + xdiff * 6 - (xdiff/2) * prop), y = c(ymin + 
                ydiff - (ydiff/2) * prop, ymin + ydiff * 2 - 
                (ydiff/2) * prop, ymin + ydiff * 3 - (ydiff/2) * 
                prop, ymin + ydiff * 4 - (ydiff/2) * prop, ymin + 
                ydiff * 5 - (ydiff/2) * prop, ymin + ydiff * 
                6 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop, xmin + 
                xdiff * 5 + (xdiff/2) * prop), y = c(ymin + (ydiff/2) * 
                prop, ymin + ydiff + (ydiff/2) * prop, ymin + 
                ydiff * 2 + (ydiff/2) * prop, ymin + ydiff * 
                3 + (ydiff/2) * prop, ymin + ydiff * 4 + (ydiff/2) * 
                prop, ymin + ydiff * 5 + (ydiff/2) * prop))
            xySubDF_1Ba <- as.data.frame(xySubBa)
            xySubDF_1Bb <- as.data.frame(xySubBb)
            xdiff <- (line3$x[2] - line3$x[1])/6
            ydiff <- (line3$y[2] - line3$y[1])/6
            xmin <- line3$x[1]
            ymin <- line3$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2, (xmin + xdiff * 5 + xmin + xdiff * 
                6)/2), y = c((ymin + ymin + ydiff)/2, (ymin + 
                ydiff + ymin + ydiff * 2)/2, (ymin + ydiff * 
                2 + ymin + ydiff * 3)/2, (ymin + ydiff * 3 + 
                ymin + ydiff * 4)/2, (ymin + ydiff * 4 + ymin + 
                ydiff * 5)/2, (ymin + ydiff * 5 + ymin + ydiff * 
                6)/2))
            xySubDF_3A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop, xmin + xdiff * 6 - (xdiff/2) * prop), y = c(ymin + 
                ydiff - (ydiff/2) * prop, ymin + ydiff * 2 - 
                (ydiff/2) * prop, ymin + ydiff * 3 - (ydiff/2) * 
                prop, ymin + ydiff * 4 - (ydiff/2) * prop, ymin + 
                ydiff * 5 - (ydiff/2) * prop, ymin + ydiff * 
                6 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop, xmin + 
                xdiff * 5 + (xdiff/2) * prop), y = c(ymin + (ydiff/2) * 
                prop, ymin + ydiff + (ydiff/2) * prop, ymin + 
                ydiff * 2 + (ydiff/2) * prop, ymin + ydiff * 
                3 + (ydiff/2) * prop, ymin + ydiff * 4 + (ydiff/2) * 
                prop, ymin + ydiff * 5 + (ydiff/2) * prop))
            xySubDF_3Ba <- as.data.frame(xySubBa)
            xySubDF_3Bb <- as.data.frame(xySubBb)
            xdiff <- (line2$x[2] - line2$x[1])/4
            ydiff <- (line2$y[2] - line2$y[1])/4
            xmin <- line2$x[1]
            ymin <- line2$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2), y = c((ymin + ymin + ydiff)/2, 
                (ymin + ydiff + ymin + ydiff * 2)/2, (ymin + 
                  ydiff * 2 + ymin + ydiff * 3)/2, (ymin + ydiff * 
                  3 + ymin + ydiff * 4)/2))
            xySubDF_2A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop), y = c(ymin + ydiff - (ydiff/2) * 
                prop, ymin + ydiff * 2 - (ydiff/2) * prop, ymin + 
                ydiff * 3 - (ydiff/2) * prop, ymin + ydiff * 
                4 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop), y = c(ymin + (ydiff/2) * prop, ymin + 
                ydiff + (ydiff/2) * prop, ymin + ydiff * 2 + 
                (ydiff/2) * prop, ymin + ydiff * 3 + (ydiff/2) * 
                prop))
            xySubDF_2Ba <- as.data.frame(xySubBa)
            xySubDF_2Bb <- as.data.frame(xySubBb)
            xdiff <- (line4$x[2] - line4$x[1])/4
            ydiff <- (line4$y[2] - line4$y[1])/4
            xmin <- line4$x[1]
            ymin <- line4$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2), y = c((ymin + ymin + ydiff)/2, 
                (ymin + ydiff + ymin + ydiff * 2)/2, (ymin + 
                  ydiff * 2 + ymin + ydiff * 3)/2, (ymin + ydiff * 
                  3 + ymin + ydiff * 4)/2))
            xySubDF_4A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop), y = c(ymin + ydiff - (ydiff/2) * 
                prop, ymin + ydiff * 2 - (ydiff/2) * prop, ymin + 
                ydiff * 3 - (ydiff/2) * prop, ymin + ydiff * 
                4 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop), y = c(ymin + (ydiff/2) * prop, ymin + 
                ydiff + (ydiff/2) * prop, ymin + ydiff * 2 + 
                (ydiff/2) * prop, ymin + ydiff * 3 + (ydiff/2) * 
                prop))
            xySubDF_4Ba <- as.data.frame(xySubBa)
            xySubDF_4Bb <- as.data.frame(xySubBb)
            points(xySubDF_1A, pch = 20, col = "green")
            points(xySubDF_1Ba, pch = 20, col = "red")
            points(xySubDF_1Bb, pch = 20, col = "red")
            points(xySubDF_2A, pch = 20, col = "green")
            points(xySubDF_2Ba, pch = 20, col = "red")
            points(xySubDF_2Bb, pch = 20, col = "red")
            points(xySubDF_3A, pch = 20, col = "green")
            points(xySubDF_3Ba, pch = 20, col = "red")
            points(xySubDF_3Bb, pch = 20, col = "red")
            points(xySubDF_4A, pch = 20, col = "green")
            points(xySubDF_4Ba, pch = 20, col = "red")
            points(xySubDF_4Bb, pch = 20, col = "red")
            labels <- list(c(1, 7, 13, 19), c(2, 8, 14, 20), 
                c(3, 9, 15, 21), c(4, 10, 16, 22), c(5, 11, 17, 
                  23), c(6, 12, 18, 24))
            xyTot <- c()
            for (e in 1:nrow(xySubDF_1A)) {
                xyLine1 <- xySubDF_1A[e, ]
                xyLine2 <- xySubDF_3A[6:1, ][e, ]
                xdiff <- (xyLine2$x - xyLine1$x)/4
                ydiff <- (xyLine2$y - xyLine1$y)/4
                xmin <- xyLine1$x
                ymin <- xyLine1$y
                xySub <- list(x = c((xmin + xmin + xdiff)/2, 
                  (xmin + xdiff + xmin + xdiff * 2)/2, (xmin + 
                    xdiff * 2 + xmin + xdiff * 3)/2, (xmin + 
                    xdiff * 3 + xmin + xdiff * 4)/2), y = c((ymin + 
                  ymin + ydiff)/2, (ymin + ydiff + ymin + ydiff * 
                  2)/2, (ymin + ydiff * 2 + ymin + ydiff * 3)/2, 
                  (ymin + ydiff * 3 + ymin + ydiff * 4)/2))
                xySubDF <- as.data.frame(xySub)
                if (is.null(colorCheckerXY)) {
                  text(xySubDF, label = labels[[e]], col = "green")
                }
                xySubDFLabel <- cbind(xySubDF, label = labels[[e]])
                xyLine1a <- xySubDF_1Ba[e, ]
                xyLine1b <- xySubDF_1Bb[e, ]
                xyLine3a <- xySubDF_3Bb[6:1, ][e, ]
                xyLine3b <- xySubDF_3Ba[6:1, ][e, ]
                xdiffa <- (xyLine3a$x - xyLine1a$x)/4
                ydiffa <- (xyLine3a$y - xyLine1a$y)/4
                xdiffb <- (xyLine3b$x - xyLine1b$x)/4
                ydiffb <- (xyLine3b$y - xyLine1b$y)/4
                xmina <- xyLine1a$x
                ymina <- xyLine1a$y
                xminb <- xyLine1b$x
                yminb <- xyLine1b$y
                xySubAa <- list(x = c(xmina + xdiffa - (xdiffa/2) * 
                  prop, xmina + xdiffa * 2 - (xdiffa/2) * prop, 
                  xmina + xdiffa * 3 - (xdiffa/2) * prop, xmina + 
                    xdiffa * 4 - (xdiffa/2) * prop), y = c(ymina + 
                  ydiffa - (ydiffa/2) * prop, ymina + ydiffa * 
                  2 - (ydiffa/2) * prop, ymina + ydiffa * 3 - 
                  (ydiffa/2) * prop, ymina + ydiffa * 4 - (ydiffa/2) * 
                  prop))
                xySubAb <- list(x = c(xmina + (xdiffa/2) * prop, 
                  xmina + xdiffa + (xdiffa/2) * prop, xmina + 
                    xdiffa * 2 + (xdiffa/2) * prop, xmina + xdiffa * 
                    3 + (xdiffa/2) * prop), y = c(ymina + (ydiffa/2) * 
                  prop, ymina + ydiffa + (ydiffa/2) * prop, ymina + 
                  ydiffa * 2 + (ydiffa/2) * prop, ymina + ydiffa * 
                  3 + (ydiffa/2) * prop))
                xySubBa <- list(x = c(xminb + xdiffb - (xdiffb/2) * 
                  prop, xminb + xdiffb * 2 - (xdiffb/2) * prop, 
                  xminb + xdiffb * 3 - (xdiffb/2) * prop, xminb + 
                    xdiffb * 4 - (xdiffb/2) * prop), y = c(yminb + 
                  ydiffb - (ydiffb/2) * prop, yminb + ydiffb * 
                  2 - (ydiffb/2) * prop, yminb + ydiffb * 3 - 
                  (ydiffb/2) * prop, yminb + ydiffb * 4 - (ydiffb/2) * 
                  prop))
                xySubBb <- list(x = c(xminb + (xdiffb/2) * prop, 
                  xminb + xdiffb + (xdiffb/2) * prop, xminb + 
                    xdiffb * 2 + (xdiffb/2) * prop, xminb + xdiffb * 
                    3 + (xdiffb/2) * prop), y = c(yminb + (ydiffb/2) * 
                  prop, yminb + ydiffb + (ydiffb/2) * prop, yminb + 
                  ydiffb * 2 + (ydiffb/2) * prop, yminb + ydiffb * 
                  3 + (ydiffb/2) * prop))
                xySubAaDF <- as.data.frame(xySubAa)
                xySubAbDF <- as.data.frame(xySubAb)
                xySubBaDF <- as.data.frame(xySubBa)
                xySubBbDF <- as.data.frame(xySubBb)
                xySubRow <- cbind(xySubAaDF, xySubAbDF, xySubBaDF, 
                  xySubBbDF, label = labels[[e]])
                colnames(xySubRow) <- c("x1", "y1", "x2", "y2", 
                  "x3", "y3", "x4", "y4", "label")
                xyTot <- rbind(xyTot, xySubRow)
            }
            xyTot$imR <- NA
            xyTot$imG <- NA
            xyTot$imB <- NA
            xyTot <- xyTot[order(xyTot$label), ]
            for (e in 1:nrow(xyTot)) {
                print(paste("Calculating observed RGB values for patch", 
                  e, sep = " "))
                polygon(c(xyTot$x1[e], xyTot$x2[e], xyTot$x4[e], 
                  xyTot$x3[e]), c(xyTot$y1[e], xyTot$y2[e], xyTot$y4[e], 
                  xyTot$y3[e]), border = "red")
                outline <- rbind(c(xyTot$x1[e], xyTot$y1[e]), 
                  c(xyTot$x2[e], xyTot$y2[e]), c(xyTot$x4[e], 
                    xyTot$y4[e]), c(xyTot$x3[e], xyTot$y3[e]))
                poly <- sp::Polygons(list(sp::Polygon(outline)), 
                  paste("r"))
                polyList <- c(poly)
                polyNames <- c(paste("r"))
                sr <- sp::SpatialPolygons(polyList)
                srdf <- sp::SpatialPolygonsDataFrame(sr, data.frame(1:length(polyNames), 
                  row.names = polyNames))
                extrR <- raster::extract(rR, srdf)
                extrG <- raster::extract(rG, srdf)
                extrB <- raster::extract(rB, srdf)
                xyTot$imR[e] <- mean(extrR[[1]])
                xyTot$imG[e] <- mean(extrG[[1]])
                xyTot$imB[e] <- mean(extrB[[1]])
            }
            l1 <- c(1, 115, 82, 68)
            l2 <- c(2, 194, 150, 130)
            l3 <- c(3, 98, 122, 157)
            l4 <- c(4, 87, 108, 67)
            l5 <- c(5, 133, 128, 177)
            l6 <- c(6, 103, 189, 170)
            l7 <- c(7, 214, 126, 44)
            l8 <- c(8, 80, 91, 166)
            l9 <- c(9, 193, 90, 99)
            l10 <- c(10, 94, 60, 108)
            l11 <- c(11, 157, 188, 64)
            l12 <- c(12, 224, 163, 46)
            l13 <- c(13, 56, 61, 150)
            l14 <- c(14, 70, 148, 73)
            l15 <- c(15, 175, 54, 60)
            l16 <- c(16, 231, 199, 31)
            l17 <- c(17, 187, 86, 149)
            l18 <- c(18, 8, 133, 161)
            l19 <- c(19, 243, 243, 242)
            l20 <- c(20, 200, 200, 200)
            l21 <- c(21, 160, 160, 160)
            l22 <- c(22, 122, 122, 121)
            l23 <- c(23, 85, 85, 85)
            l24 <- c(24, 52, 52, 52)
            ColorCheckerRGB <- as.data.frame(rbind(l1, l2, l3, 
                l4, l5, l6, l7, l8, l9, l10, l11, l12, l13, l14, 
                l15, l16, l17, l18, l19, l20, l21, l22, l23, 
                l24))
            colnames(ColorCheckerRGB) <- c("label", "sR", "sG", 
                "sB")
            dat <- merge(xyTot, ColorCheckerRGB, by = "label")
            print("Calculating polynomial regression...")
            sR <- dat$sR
            sG <- dat$sG
            sB <- dat$sB
            imR <- dat$imR
            imG <- dat$imG
            imB <- dat$imB
            modelR <- lm(sR ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            modelG <- lm(sG ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            modelB <- lm(sB ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            dfIm = data.frame(imR = matrix(mR, ncol = 1), imG = matrix(mG, 
                ncol = 1), imB = matrix(mB, ncol = 1))
            print("Calibrating colors...")
            prR <- predict(modelR, dfIm)
            prG <- predict(modelG, dfIm)
            prB <- predict(modelB, dfIm)
            dfCal <- as.data.frame(cbind(prR, prG, prB))
            print("Rebuilding image...")
            Ri = matrix(dfCal$prR, nrow = dim(imRed)[1])
            Gi = matrix(dfCal$prG, nrow = dim(imRed)[1])
            Bi = matrix(dfCal$prB, nrow = dim(imRed)[1])
            imCal = array(dim = dim(imRed))
            imCal[, , , 1] = Ri
            imCal[, , , 2] = Gi
            imCal[, , , 3] = Bi
            imCal <- imager::as.cimg(imCal)
            layout(matrix(c(1, 2), 2, 1, byrow = TRUE))
            plot(imRed)
            plot(imCal)
        }
        if (all(c(colorCheckerType == "ColorGauge Micro Analyzer", 
            is.null(fixedModel)))) {
            if (is.null(colorCheckerXY)) {
                print("Click on the outer corners of the ColorGauge Micro Analyzer ColorChecker (1: ~brown, 2: ~cyan, 3: ~purple, 4: ~red)")
                layout(matrix(c(1, 1), 2, 1, byrow = TRUE))
                plot(imRed, xlim = c(0, width(imRed)))
                if (fixedCorners == FALSE) {
                  xy <- locator(n = 4)
                }
                if (all(c(fixedCorners == TRUE & n == 1))) {
                  xy <- locator(n = 4)
                }
            }
            if (!is.null(colorCheckerXY)) {
                xy <- list()
                xy$x <- colorCheckerXY[[n]][, 1]
                xy$y <- colorCheckerXY[[n]][, 2]
            }
            print("Matching ColorCecker patches...")
            if (is.null(colorCheckerXY)) {
                polygon(xy$x, xy$y, border = "green")
            }
            xyDF <- as.data.frame(xy)
            line1 <- xyDF[1:2, ]
            line2 <- xyDF[2:3, ]
            line3 <- xyDF[3:4, ]
            line4 <- xyDF[c(4, 1), ]
            xdiff <- (line1$x[2] - line1$x[1])/6
            ydiff <- (line1$y[2] - line1$y[1])/6
            xmin <- line1$x[1]
            ymin <- line1$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2, (xmin + xdiff * 5 + xmin + xdiff * 
                6)/2), y = c((ymin + ymin + ydiff)/2, (ymin + 
                ydiff + ymin + ydiff * 2)/2, (ymin + ydiff * 
                2 + ymin + ydiff * 3)/2, (ymin + ydiff * 3 + 
                ymin + ydiff * 4)/2, (ymin + ydiff * 4 + ymin + 
                ydiff * 5)/2, (ymin + ydiff * 5 + ymin + ydiff * 
                6)/2))
            xySubDF_1A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop, xmin + xdiff * 6 - (xdiff/2) * prop), y = c(ymin + 
                ydiff - (ydiff/2) * prop, ymin + ydiff * 2 - 
                (ydiff/2) * prop, ymin + ydiff * 3 - (ydiff/2) * 
                prop, ymin + ydiff * 4 - (ydiff/2) * prop, ymin + 
                ydiff * 5 - (ydiff/2) * prop, ymin + ydiff * 
                6 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop, xmin + 
                xdiff * 5 + (xdiff/2) * prop), y = c(ymin + (ydiff/2) * 
                prop, ymin + ydiff + (ydiff/2) * prop, ymin + 
                ydiff * 2 + (ydiff/2) * prop, ymin + ydiff * 
                3 + (ydiff/2) * prop, ymin + ydiff * 4 + (ydiff/2) * 
                prop, ymin + ydiff * 5 + (ydiff/2) * prop))
            xySubDF_1Ba <- as.data.frame(xySubBa)
            xySubDF_1Bb <- as.data.frame(xySubBb)
            xdiff <- (line3$x[2] - line3$x[1])/6
            ydiff <- (line3$y[2] - line3$y[1])/6
            xmin <- line3$x[1]
            ymin <- line3$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2, (xmin + xdiff * 5 + xmin + xdiff * 
                6)/2), y = c((ymin + ymin + ydiff)/2, (ymin + 
                ydiff + ymin + ydiff * 2)/2, (ymin + ydiff * 
                2 + ymin + ydiff * 3)/2, (ymin + ydiff * 3 + 
                ymin + ydiff * 4)/2, (ymin + ydiff * 4 + ymin + 
                ydiff * 5)/2, (ymin + ydiff * 5 + ymin + ydiff * 
                6)/2))
            xySubDF_3A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop, xmin + xdiff * 6 - (xdiff/2) * prop), y = c(ymin + 
                ydiff - (ydiff/2) * prop, ymin + ydiff * 2 - 
                (ydiff/2) * prop, ymin + ydiff * 3 - (ydiff/2) * 
                prop, ymin + ydiff * 4 - (ydiff/2) * prop, ymin + 
                ydiff * 5 - (ydiff/2) * prop, ymin + ydiff * 
                6 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop, xmin + 
                xdiff * 5 + (xdiff/2) * prop), y = c(ymin + (ydiff/2) * 
                prop, ymin + ydiff + (ydiff/2) * prop, ymin + 
                ydiff * 2 + (ydiff/2) * prop, ymin + ydiff * 
                3 + (ydiff/2) * prop, ymin + ydiff * 4 + (ydiff/2) * 
                prop, ymin + ydiff * 5 + (ydiff/2) * prop))
            xySubDF_3Ba <- as.data.frame(xySubBa)
            xySubDF_3Bb <- as.data.frame(xySubBb)
            xdiff <- (line2$x[2] - line2$x[1])/5
            ydiff <- (line2$y[2] - line2$y[1])/5
            xmin <- line2$x[1]
            ymin <- line2$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2), y = c((ymin + ymin + ydiff)/2, 
                (ymin + ydiff + ymin + ydiff * 2)/2, (ymin + 
                  ydiff * 2 + ymin + ydiff * 3)/2, (ymin + ydiff * 
                  3 + ymin + ydiff * 4)/2, (ymin + ydiff * 4 + 
                  ymin + ydiff * 5)/2))
            xySubDF_2A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop), y = c(ymin + ydiff - (ydiff/2) * prop, 
                ymin + ydiff * 2 - (ydiff/2) * prop, ymin + ydiff * 
                  3 - (ydiff/2) * prop, ymin + ydiff * 4 - (ydiff/2) * 
                  prop, ymin + ydiff * 5 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop), y = c(ymin + 
                (ydiff/2) * prop, ymin + ydiff + (ydiff/2) * 
                prop, ymin + ydiff * 2 + (ydiff/2) * prop, ymin + 
                ydiff * 3 + (ydiff/2) * prop, ymin + ydiff * 
                4 + (ydiff/2) * prop))
            xySubDF_2Ba <- as.data.frame(xySubBa)
            xySubDF_2Bb <- as.data.frame(xySubBb)
            xdiff <- (line4$x[2] - line4$x[1])/5
            ydiff <- (line4$y[2] - line4$y[1])/5
            xmin <- line4$x[1]
            ymin <- line4$y[1]
            xySubA <- list(x = c((xmin + xmin + xdiff)/2, (xmin + 
                xdiff + xmin + xdiff * 2)/2, (xmin + xdiff * 
                2 + xmin + xdiff * 3)/2, (xmin + xdiff * 3 + 
                xmin + xdiff * 4)/2, (xmin + xdiff * 4 + xmin + 
                xdiff * 5)/2), y = c((ymin + ymin + ydiff)/2, 
                (ymin + ydiff + ymin + ydiff * 2)/2, (ymin + 
                  ydiff * 2 + ymin + ydiff * 3)/2, (ymin + ydiff * 
                  3 + ymin + ydiff * 4)/2, (ymin + ydiff * 4 + 
                  ymin + ydiff * 5)/2))
            xySubDF_4A <- as.data.frame(xySubA)
            xySubBa <- list(x = c(xmin + xdiff - (xdiff/2) * 
                prop, xmin + xdiff * 2 - (xdiff/2) * prop, xmin + 
                xdiff * 3 - (xdiff/2) * prop, xmin + xdiff * 
                4 - (xdiff/2) * prop, xmin + xdiff * 5 - (xdiff/2) * 
                prop), y = c(ymin + ydiff - (ydiff/2) * prop, 
                ymin + ydiff * 2 - (ydiff/2) * prop, ymin + ydiff * 
                  3 - (ydiff/2) * prop, ymin + ydiff * 4 - (ydiff/2) * 
                  prop, ymin + ydiff * 5 - (ydiff/2) * prop))
            xySubBb <- list(x = c(xmin + (xdiff/2) * prop, xmin + 
                xdiff + (xdiff/2) * prop, xmin + xdiff * 2 + 
                (xdiff/2) * prop, xmin + xdiff * 3 + (xdiff/2) * 
                prop, xmin + xdiff * 4 + (xdiff/2) * prop), y = c(ymin + 
                (ydiff/2) * prop, ymin + ydiff + (ydiff/2) * 
                prop, ymin + ydiff * 2 + (ydiff/2) * prop, ymin + 
                ydiff * 3 + (ydiff/2) * prop, ymin + ydiff * 
                4 + (ydiff/2) * prop))
            xySubDF_4Ba <- as.data.frame(xySubBa)
            xySubDF_4Bb <- as.data.frame(xySubBb)
            if (is.null(colorCheckerXY)) {
                points(xySubDF_1A, pch = 20, col = "green")
                points(xySubDF_1Ba, pch = 20, col = "red")
                points(xySubDF_1Bb, pch = 20, col = "red")
                points(xySubDF_2A, pch = 20, col = "green")
                points(xySubDF_2Ba, pch = 20, col = "red")
                points(xySubDF_2Bb, pch = 20, col = "red")
                points(xySubDF_3A, pch = 20, col = "green")
                points(xySubDF_3Ba, pch = 20, col = "red")
                points(xySubDF_3Bb, pch = 20, col = "red")
                points(xySubDF_4A, pch = 20, col = "green")
                points(xySubDF_4Ba, pch = 20, col = "red")
                points(xySubDF_4Bb, pch = 20, col = "red")
            }
            labels <- list(c(1, 7, 13, 19, 25), c(2, 8, 14, 20, 
                26), c(3, 9, 15, 21, 27), c(4, 10, 16, 22, 28), 
                c(5, 11, 17, 23, 29), c(6, 12, 18, 24, 30))
            xyTot <- c()
            for (e in 1:nrow(xySubDF_1A)) {
                xyLine1 <- xySubDF_1A[e, ]
                xyLine2 <- xySubDF_3A[6:1, ][e, ]
                xdiff <- (xyLine2$x - xyLine1$x)/5
                ydiff <- (xyLine2$y - xyLine1$y)/5
                xmin <- xyLine1$x
                ymin <- xyLine1$y
                xySub <- list(x = c((xmin + xmin + xdiff)/2, 
                  (xmin + xdiff + xmin + xdiff * 2)/2, (xmin + 
                    xdiff * 2 + xmin + xdiff * 3)/2, (xmin + 
                    xdiff * 3 + xmin + xdiff * 4)/2, (xmin + 
                    xdiff * 4 + xmin + xdiff * 5)/2), y = c((ymin + 
                  ymin + ydiff)/2, (ymin + ydiff + ymin + ydiff * 
                  2)/2, (ymin + ydiff * 2 + ymin + ydiff * 3)/2, 
                  (ymin + ydiff * 3 + ymin + ydiff * 4)/2, (ymin + 
                    ydiff * 4 + ymin + ydiff * 5)/2))
                xySubDF <- as.data.frame(xySub)
                if (is.null(colorCheckerXY)) {
                  text(xySubDF, label = labels[[e]], col = "green")
                }
                xySubDFLabel <- cbind(xySubDF, label = labels[[e]])
                xyLine1a <- xySubDF_1Ba[e, ]
                xyLine1b <- xySubDF_1Bb[e, ]
                xyLine3a <- xySubDF_3Bb[6:1, ][e, ]
                xyLine3b <- xySubDF_3Ba[6:1, ][e, ]
                xdiffa <- (xyLine3a$x - xyLine1a$x)/5
                ydiffa <- (xyLine3a$y - xyLine1a$y)/5
                xdiffb <- (xyLine3b$x - xyLine1b$x)/5
                ydiffb <- (xyLine3b$y - xyLine1b$y)/5
                xmina <- xyLine1a$x
                ymina <- xyLine1a$y
                xminb <- xyLine1b$x
                yminb <- xyLine1b$y
                xySubAa <- list(x = c(xmina + xdiffa - (xdiffa/2) * 
                  prop, xmina + xdiffa * 2 - (xdiffa/2) * prop, 
                  xmina + xdiffa * 3 - (xdiffa/2) * prop, xmina + 
                    xdiffa * 4 - (xdiffa/2) * prop, xmina + xdiffa * 
                    5 - (xdiffa/2) * prop), y = c(ymina + ydiffa - 
                  (ydiffa/2) * prop, ymina + ydiffa * 2 - (ydiffa/2) * 
                  prop, ymina + ydiffa * 3 - (ydiffa/2) * prop, 
                  ymina + ydiffa * 4 - (ydiffa/2) * prop, ymina + 
                    ydiffa * 5 - (ydiffa/2) * prop))
                xySubAb <- list(x = c(xmina + (xdiffa/2) * prop, 
                  xmina + xdiffa + (xdiffa/2) * prop, xmina + 
                    xdiffa * 2 + (xdiffa/2) * prop, xmina + xdiffa * 
                    3 + (xdiffa/2) * prop, xmina + xdiffa * 4 + 
                    (xdiffa/2) * prop), y = c(ymina + (ydiffa/2) * 
                  prop, ymina + ydiffa + (ydiffa/2) * prop, ymina + 
                  ydiffa * 2 + (ydiffa/2) * prop, ymina + ydiffa * 
                  3 + (ydiffa/2) * prop, ymina + ydiffa * 4 + 
                  (ydiffa/2) * prop))
                xySubBa <- list(x = c(xminb + xdiffb - (xdiffb/2) * 
                  prop, xminb + xdiffb * 2 - (xdiffb/2) * prop, 
                  xminb + xdiffb * 3 - (xdiffb/2) * prop, xminb + 
                    xdiffb * 4 - (xdiffb/2) * prop, xminb + xdiffb * 
                    5 - (xdiffb/2) * prop), y = c(yminb + ydiffb - 
                  (ydiffb/2) * prop, yminb + ydiffb * 2 - (ydiffb/2) * 
                  prop, yminb + ydiffb * 3 - (ydiffb/2) * prop, 
                  yminb + ydiffb * 4 - (ydiffb/2) * prop, yminb + 
                    ydiffb * 5 - (ydiffb/2) * prop))
                xySubBb <- list(x = c(xminb + (xdiffb/2) * prop, 
                  xminb + xdiffb + (xdiffb/2) * prop, xminb + 
                    xdiffb * 2 + (xdiffb/2) * prop, xminb + xdiffb * 
                    3 + (xdiffb/2) * prop, xminb + xdiffb * 4 + 
                    (xdiffb/2) * prop), y = c(yminb + (ydiffb/2) * 
                  prop, yminb + ydiffb + (ydiffb/2) * prop, yminb + 
                  ydiffb * 2 + (ydiffb/2) * prop, yminb + ydiffb * 
                  3 + (ydiffb/2) * prop, yminb + ydiffb * 4 + 
                  (ydiffb/2) * prop))
                xySubAaDF <- as.data.frame(xySubAa)
                xySubAbDF <- as.data.frame(xySubAb)
                xySubBaDF <- as.data.frame(xySubBa)
                xySubBbDF <- as.data.frame(xySubBb)
                xySubRow <- cbind(xySubAaDF, xySubAbDF, xySubBaDF, 
                  xySubBbDF, label = labels[[e]])
                colnames(xySubRow) <- c("x1", "y1", "x2", "y2", 
                  "x3", "y3", "x4", "y4", "label")
                xyTot <- rbind(xyTot, xySubRow)
            }
            xyTot$imR <- NA
            xyTot$imG <- NA
            xyTot$imB <- NA
            xyTot <- xyTot[order(xyTot$label), ]
            for (e in 1:nrow(xyTot)) {
                print(paste("Calculating observed RGB values for patch", 
                  e, sep = " "))
                if (is.null(colorCheckerXY)) {
                  polygon(c(xyTot$x1[e], xyTot$x2[e], xyTot$x4[e], 
                    xyTot$x3[e]), c(xyTot$y1[e], xyTot$y2[e], 
                    xyTot$y4[e], xyTot$y3[e]), border = "red")
                }
                outline <- rbind(c(xyTot$x1[e], xyTot$y1[e]), 
                  c(xyTot$x2[e], xyTot$y2[e]), c(xyTot$x4[e], 
                    xyTot$y4[e]), c(xyTot$x3[e], xyTot$y3[e]))
                poly <- sp::Polygons(list(sp::Polygon(outline)), 
                  paste("r"))
                polyList <- c(poly)
                polyNames <- c(paste("r"))
                sr <- sp::SpatialPolygons(polyList)
                srdf <- sp::SpatialPolygonsDataFrame(sr, data.frame(1:length(polyNames), 
                  row.names = polyNames))
                extrR <- raster::extract(rR, srdf)
                extrG <- raster::extract(rG, srdf)
                extrB <- raster::extract(rB, srdf)
                xyTot$imR[e] <- mean(extrR[[1]])
                xyTot$imG[e] <- mean(extrG[[1]])
                xyTot$imB[e] <- mean(extrB[[1]])
            }
            l1 <- c(1, 116, 91, 76)
            l2 <- c(2, 192, 158, 141)
            l3 <- c(3, 113, 128, 160)
            l4 <- c(4, 104, 118, 72)
            l5 <- c(5, 141, 135, 181)
            l6 <- c(6, 144, 195, 179)
            l7 <- c(7, 79, 141, 173)
            l8 <- c(8, 243, 244, 240)
            l9 <- c(9, 234, 235, 232)
            l10 <- c(10, 221, 222, 220)
            l11 <- c(11, 209, 211, 209)
            l12 <- c(12, 203, 138, 65)
            l13 <- c(13, 178, 93, 158)
            l14 <- c(14, 183, 185, 184)
            l15 <- c(15, 158, 160, 159)
            l16 <- c(16, 125, 127, 127)
            l17 <- c(17, 99, 99, 99)
            l18 <- c(18, 89, 94, 173)
            l19 <- c(19, 227, 209, 65)
            l20 <- c(20, 72, 74, 73)
            l21 <- c(21, 46, 46, 46)
            l22 <- c(22, 25, 24, 24)
            l23 <- c(23, 11, 11, 12)
            l24 <- c(24, 179, 95, 108)
            l25 <- c(25, 162, 66, 68)
            l26 <- c(26, 110, 159, 84)
            l27 <- c(27, 61, 63, 150)
            l28 <- c(28, 214, 174, 66)
            l29 <- c(29, 175, 197, 84)
            l30 <- c(30, 93, 61, 108)
            ColorCheckerRGB <- as.data.frame(rbind(l1, l2, l3, 
                l4, l5, l6, l7, l8, l9, l10, l11, l12, l13, l14, 
                l15, l16, l17, l18, l19, l20, l21, l22, l23, 
                l24, l25, l26, l27, l28, l29, l30))
            colnames(ColorCheckerRGB) <- c("label", "sR", "sG", 
                "sB")
            dat <- merge(xyTot, ColorCheckerRGB, by = "label")
            print("Calculating polynomial regression...")
            sR <- dat$sR
            sG <- dat$sG
            sB <- dat$sB
            imR <- dat$imR
            imG <- dat$imG
            imB <- dat$imB
            modelR <- lm(sR ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            modelG <- lm(sG ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            modelB <- lm(sB ~ imR + imG + imB + imR^2 + imG^2 + 
                imB^2)
            dfIm = data.frame(imR = matrix(mR, ncol = 1), imG = matrix(mG, 
                ncol = 1), imB = matrix(mB, ncol = 1))
            print("Calibrating colors...")
            prR <- predict(modelR, dfIm)
            prG <- predict(modelG, dfIm)
            prB <- predict(modelB, dfIm)
            dfCal <- as.data.frame(cbind(prR, prG, prB))
            print("Rebuilding image...")
            Ri = matrix(dfCal$prR, nrow = dim(im)[1])
            Gi = matrix(dfCal$prG, nrow = dim(im)[1])
            Bi = matrix(dfCal$prB, nrow = dim(im)[1])
            imCal = array(dim = dim(im))
            imCal[, , , 1] = Ri
            imCal[, , , 2] = Gi
            imCal[, , , 3] = Bi
            imCal <- imager::as.cimg(imCal)
            if (is.null(colorCheckerXY)) {
                layout(matrix(c(1, 2), 2, 1, byrow = TRUE))
                plot(imRed)
                plot(imCal)
            }
        }
        if (!is.null(fixedModel)) {
            modelR <- fixedModel[[1]]
            modelG <- fixedModel[[2]]
            modelB <- fixedModel[[3]]
            dfIm = data.frame(imR = matrix(mR, ncol = 1), imG = matrix(mG, 
                ncol = 1), imB = matrix(mB, ncol = 1))
            print("Calibrating colors...")
            prR <- predict(modelR, dfIm)
            prG <- predict(modelG, dfIm)
            prB <- predict(modelB, dfIm)
            dfCal <- as.data.frame(cbind(prR, prG, prB))
            print("Rebuilding image...")
            Ri = matrix(dfCal$prR, nrow = dim(imRed)[1])
            Gi = matrix(dfCal$prG, nrow = dim(imRed)[1])
            Bi = matrix(dfCal$prB, nrow = dim(imRed)[1])
            imCal = array(dim = dim(imRed))
            imCal[, , , 1] = Ri
            imCal[, , , 2] = Gi
            imCal[, , , 3] = Bi
            imCal <- imager::as.cimg(imCal)
        }
        if (is.null(outpath)) {
            im <- imager::save.image(imCal, paste(IDlist[n], 
                "_calibrated", extension, sep = ""), quality = 1)
        }
        else {
            im <- imager::save.image(imCal, paste(outpath, "/", 
                IDlist[n], "_calibrated", extension, sep = ""), 
                quality = 1)
        }
    }
    return(list(modelR, modelG, modelB))
}
```

#Finding all parameters for colorChecker
```{r, include=FALSE, echo=FALSE}
pre = "JPEG_image"
out = "Calibrated_image"
ext = ".jpeg"
  
# fichiers <- list.files(path="TIFF_image", pattern=".tiff", full.names = TRUE)
# 
# for (im in fichiers){
#   tiff <- readTIFF(im, native=FALSE)
#   targ = paste0(pre, substr(im,12,nchar(im)-5),".jpeg")
#   writeJPEG(tiff, target=targ, quality = 1)
# }

fichiers2 <- list.files(path="JPEG_image", pattern=".jpeg", full.names = FALSE)

for (i in 1:length(fichiers2)){
  fichiers2[i] <- strtrim(fichiers2[i], nchar(fichiers2[i])-5)
}

fichiers2 <- fichiers2[2:length(fichiers2)]
```

#TO RUN IN THE CONSOLE with the right wd !
```{r, include=FALSE, echo=FALSE}
colorChecker2(fichiers2, prepath=pre, outpath = out, extension=".jpeg")
```

#cropping images for just butterfly wings
```{r, include=FALSE, echo=FALSE}
fichiers3 <- list.files(path="Calibrated_image", pattern=".jpeg", full.names = FALSE)

for (path in fichiers3){
  name <- str_remove(path, "_calibrated")
  im <- image_read(paste0(out,"/",path))
  crop_im <- image_crop(im, "2400x2330+400+170")
  image_write(crop_im, paste0("Cropped_image/", name), format = "jpeg")
  gc()
}
```

#Landmarks from csv to txt
```{r, include=FALSE, echo=FALSE}
#extracting or specifying IDs
IDlist <- c("FG24.041_D", "FG24.045_D", "FG24.046_D", "FG24.047_D", "FG24.048_D", "FG24.051_D", "FG24.052_D", "FG24.053_D", "FG24.054_D", "FG24.055_D", "FG24.061_D", "FG24.062_D", "FG24.063_D", "FG24.064_D", "FG24.065_D", "FG24.066_D", "FG24.067_D", "FG24.068_D", "FG24.069_D", "FG24.070_D", "FG24.071_D", "FG24.072_D", "FG24.073_D", "FG24.074_D", "FG24.075_D", "FG24.076_D", "FG24.084_D", "FG24.085_D", "FG24.086_D", "FG24.087_D", "FG24.088_D")

#changing landmarks to txt format with just X and y columns
for (ID in IDlist){
  temp_df <- read.csv(paste0("Landmarks.csv/",ID,"_landmarks.csv"), header = TRUE)
  txt_df <- temp_df[,c(6,7)]
  write.table(txt_df, paste0("Landmarks/",ID,"_landmarks.txt"), col.names = FALSE, row.names = FALSE)
  temp_df <- read.csv(paste0("Landmarks.csv/",ID,"_landmarks2.csv"), header = TRUE)
  txt_df <- temp_df[,c(6,7)]
  write.table(txt_df, paste0("Landmarks/",ID,"_landmarks2.txt"), col.names = FALSE, row.names = FALSE)
}

mask_name <- c("FG24.087_D_Lforewing", "FG24.087_D_Lhindwing")
#same for the four masks files
for (mask in mask_name){
  temp_df <- read.csv(paste0("Landmarks.csv/mask/",mask,".csv"), header = TRUE)
  txt_df <- temp_df[,c(6,7)]
  write.table(txt_df, paste0("Landmarks/mask/",mask,".txt"), col.names = FALSE, row.names = FALSE)
}
```

#Preparing the lists for aligning images
```{r, include=FALSE, echo=FALSE}
#making the lists for patternize
wings_list <- makeList(IDlist, type = "image", prepath = "Cropped_image/", extension=".jpeg")

landmarkList <- makeList(IDlist, type = "landmark", prepath = "Landmarks/", extension = "_landmarks.txt")
landmarkhindList <- makeList(IDlist, type = "landmark", prepath = "Landmarks/", extension = "_landmarks2.txt")

#set target as ID 87
target <- landmarkList[["FG24.087_D"]]
target2 <- landmarkhindList[["FG24.087_D"]]

#Setting up the masks that keeps the 4 wings and exclude the background
mask1 <- read.table("Landmarks/mask/FG24.087_D_Lforewing.txt", header=FALSE)
mask2 <- read.table("Landmarks/mask/FG24.087_D_Lhindwing.txt", header=FALSE)
```

#Aligning images
```{r, include=FALSE, echo=FALSE}
#aligning the wings
imageList_aligned <- alignLan(wings_list, landmarkList, transformRef = target,
                              adjustCoords = FALSE,
                              plotTransformed = T,
                              resampleFactor = 5,
                              cartoonID = ('FG24.087_D'),
                              maskOutline = mask1,
                              inverse = FALSE,
                              removebg = 170)

aligned_85 <- alignLan(wings_list[c("FG24.085_D","FG24.087_D")], landmarkList[c("FG24.085_D","FG24.087_D")], transformRef = target,
                              adjustCoords = FALSE,
                              plotTransformed = T,
                              resampleFactor = 5,
                              cartoonID = ('FG24.087_D'),
                              maskOutline = mask1,
                              inverse = FALSE,
                              removebg = 190)

imageList_aligned["FG24.085_D"] <- aligned_85["FG24.085_D"]

hind_aligned <- alignLan(wings_list, landmarkhindList, transformRef = target2,
                              adjustCoords = FALSE,
                              plotTransformed = T,
                              resampleFactor = 5,
                              cartoonID = ('FG24.087_D'),
                              maskOutline = mask2,
                              inverse = FALSE,
                              removebg = 186)
# save RDS file
saveRDS(imageList_aligned, "rds_file/imageList_aligned.rds")
saveRDS(hind_aligned, "rds_file/hind_aligned.rds")
```

#Selecting the color palette to work with forewings
```{r, include=FALSE, echo=FALSE}
#loading images
imageList_aligned <- readRDS("rds_file/imageList_aligned.rds")

#loading the package
library(recolorize)

# convert from RasterBricks to image arrays using the brick_to_array function
imgs <- lapply(imageList_aligned, brick_to_array)
names(imgs) <- names(imageList_aligned)

# save raster extents for later conversion:
extent_list <- lapply(imageList_aligned, raster::extent)

# make an empty list for storing the recolorize objects
rc_list <- vector("list", length(imgs))
names(rc_list) <- names(imgs)

for (i in 1:length(imgs)) {
  rc_list[[i]] <- recolorize2(imgs[[i]], method = "kmeans", n=3,
                              plotting = FALSE)
}

# get a dataframe of all colors:
all_palettes <- do.call(rbind, lapply(rc_list, function(i) i$centers))

# and for cluster sizes (as a proportion of their original image):
all_sizes <- do.call(cbind, lapply(rc_list, function(i) i$sizes))

# plot colors using hclust and return grouping list:
par(mar = rep(2, 4))
cluster_list <- hclust_color(all_palettes, n_final = 4)

# make an empty matrix for storing the new palette
morpho_palette <- matrix(NA, ncol = 3, nrow = length(cluster_list))

# for every color in cluster_list...
for (i in 1:length(cluster_list)) {
  
  # get the center indices
  idx <- cluster_list[[i]]
  
  # get the average value for each channel, using cluster size to get a weighted average
  ctr <- apply(all_palettes, 2, 
                 function(j) weighted.mean(j[idx], 
                                           w = all_sizes[idx]))
  
  # store in the palette matrix
  morpho_palette[i, ] <- ctr
}

# check that our colors seem reasonable
par(mar = rep(0, 4))
plotColorPalette(morpho_palette)

morpho_palette2 <- morpho_palette
morpho_palette2[1,] <- c(0.3176471, 0.3607843, 0.36862745)
morpho_palette2[2,] <- c(0.5130015, 0.5353847, 0.48962950)
morpho_palette2[3,] <- c(0.1433055, 0.1026748, 0.09598966)
morpho_palette2[4,] <- c(0.5137255, 0.3568627, 0.11764706)

plotColorPalette(morpho_palette2)

impose_list <- lapply(imgs, function(i) imposeColors(i, morpho_palette2, 
                                                     adjust_centers = FALSE, 
                                                     plotting = FALSE))

for (i in 1:length(impose_list)) {
  plot(impose_list[[i]])
}

# # let's look at our palettes!
# layout(matrix(1:20, nrow = 4))
# par(mar = rep(0, 4))
# for (i in impose_list) {
#   plotColorPalette(i$centers, i$sizes)
# }
```

#Selecting the color palette to work with for hindwings
```{r, include=FALSE, echo=FALSE}
#loading images
hind_aligned <- readRDS("rds_file/hind_aligned.rds")

#loading the package
library(recolorize)

# convert from RasterBricks to image arrays using the brick_to_array function
imgs_hind <- lapply(hind_aligned, brick_to_array)
names(imgs_hind) <- names(hind_aligned)

# save raster extents for later conversion:
extent_list_hind <- lapply(hind_aligned, raster::extent)

# make an empty list for storing the recolorize objects
rc_list_hind <- vector("list", length(imgs_hind))
names(rc_list_hind) <- names(imgs_hind)

for (i in 1:length(imgs_hind)) {
  rc_list_hind[[i]] <- recolorize2(imgs_hind[[i]], method = "kmeans", n=5,
                              plotting = FALSE)
}

# get a dataframe of all colors:
all_palettes_hind <- do.call(rbind, lapply(rc_list_hind, function(i) i$centers))

# and for cluster sizes (as a proportion of their original image):
all_sizes_hind <- do.call(cbind, lapply(rc_list_hind, function(i) i$sizes))

# plot colors using hclust and return grouping list:
par(mar = rep(2, 4))
cluster_list_hind <- hclust_color(all_palettes_hind, n_final = 4)

# make an empty matrix for storing the new palette
morpho_palette_hind <- matrix(NA, ncol = 3, nrow = length(cluster_list_hind))

# for every color in cluster_list...
for (i in 1:length(cluster_list_hind)) {
  
  # get the center indices
  idx <- cluster_list_hind[[i]]
  
  # get the average value for each channel, using cluster size to get a weighted average
  ctr <- apply(all_palettes_hind, 2, 
                 function(j) weighted.mean(j[idx], 
                                           w = all_sizes_hind[idx]))
  
  # store in the palette matrix
  morpho_palette_hind[i, ] <- ctr
}

# check that our colors seem reasonable
par(mar = rep(0, 4))
plotColorPalette(morpho_palette_hind)

morpho_palette2_hind <- morpho_palette_hind[-3,]
morpho_palette2_hind[1,] <- c(0.5561577, 0.56080639, 0.50203665)
morpho_palette2_hind[2,] <- c(0.1223087, 0.08726718, 0.08392289)
morpho_palette2_hind[3,] <- c(0.4811294, 0.40107321, 0.26685166)
plotColorPalette(morpho_palette2_hind)

morpho_palette2_hind[1,] <- c(0.5130015, 0.5353847, 0.48962950)
morpho_palette2_hind[2,] <- c(0.1433055, 0.1026748, 0.09598966)
morpho_palette2_hind[3,] <- c(0.5137255, 0.3568627, 0.11764706)
plotColorPalette(morpho_palette2_hind)

impose_list_hind <- lapply(imgs_hind, function(i) imposeColors(i, morpho_palette2_hind, 
                                                     adjust_centers = FALSE, 
                                                     plotting = FALSE))

for (i in 1:length(impose_list_hind)) {
  plot(impose_list_hind[[i]])
}

# # let's look at our palettes!
# layout(matrix(1:20, nrow = 4))
# par(mar = rep(0, 4))
# for (i in impose_list) {
#   plotColorPalette(i$centers, i$sizes)
# }
```

#Recolor_selection function
```{r}
#loading images
imageList_aligned <- readRDS("rds_file/imageList_aligned.rds")

recolor_selection <- function(rc_obj, color_to = 1, 
                       selection = "rect", 
                       locator_color = "red",
                       n_polygons = 1,
                       plotting = TRUE,
                       recolor_background = FALSE) {
  # store old map
  rc_original_pix <- rc_obj$pixel_assignments
  
  # choose region selection method:
  selection <- match.arg(arg = selection, choices = c("rectangle", "polygon"))
  
  # make image:
  img <- recoloredImage(rc_obj, type = "raster")
  layout(1); par(mar = rep(0, 4))
  plot(img)
  
  # plot horizontal and vertical bounds to keep user from selecting
  # outside the image boundaries:
  abline(h = c(0, dim(img)[1]), v = c(0, dim(img)[2]), col = "darkgrey")
  
  # user-select area and change color of pixels inside region of interest
  if (selection == "rectangle") {
    
    # select a rectangle
    u <- spatstat.geom::clickbox(add = TRUE, col = locator_color)
    
    # store the input
    u$xrange <- round(u$xrange)
    u$yrange <- round(u$yrange)
    
    # flip the yrange (in the image, y is numbered bottom to top, but in an array
    # it's indexed top to bottom)
    u$yrange <- dim(img)[1] - u$yrange
    
    # and change pixel assignments to new color
    rc_obj$pixel_assignments[u$yrange[1]:u$yrange[2],
                             u$xrange[1]:u$xrange[2]] <- color_to
    
  } else if (selection == "polygon") {
    
    # select polygon(s)
    u <- spatstat.geom::clickpoly(add = TRUE, col = locator_color, np = n_polygons)
    u$xrange <- round(u$xrange)
    u$yrange <- round(u$yrange)
    u$bdry <- lapply(u$bdry, \(x) lapply(x, round))
    
    # find all pixels inside of the bounding box for the polygon(s)
    xy <- expand.grid(u$xrange[1]:u$xrange[2], u$yrange[1]:u$yrange[2])
    
    # for every polygon...
    for (i in 1:length(u$bdry)) {
      pol <- u$bdry[[i]]
      # find which points in the bounding box fall inside the polygon
      if (i == 1) {
        col_idx <- xy[which(secr::pointsInPolygon(xy, do.call(cbind, pol), logical = T)), ]
      } else {
        new_idx <- xy[which(secr::pointsInPolygon(xy, do.call(cbind, pol), logical = T)), ]
        col_idx <- rbind(col_idx, new_idx)
      }
    }
      
      # reverse x/y order, y
      col_idx <- as.matrix(col_idx[ , 2:1])
      col_idx[,1] <- dim(img)[1] - col_idx[,1]
      
      # and change color
      rc_obj$pixel_assignments[col_idx] <- color_to
      
  }
  
  # make sure the background is still transparent
  if (!recolor_background) {
    rc_obj$pixel_assignments[rc_original_pix == 0] <- 0
  }
  
  # if plotting, plot
  if (plotting) {
    
    # draw box or polygon around the region that was changed
    plot_region <- function() {
      xdim <- dim(rc_obj$pixel_assignments)[2]
      ydim <- dim(rc_obj$pixel_assignments)[1]
      if (selection == "rectangle") {
        rect(xleft = u$xrange[1] / xdim, xright = u$xrange[2] / xdim,
             ybottom = 1 - u$yrange[1] / ydim, ytop = 1 - u$yrange[2] / ydim,
             border = locator_color)
      } else {
        for (i in 1:length(u$bdry)) {
          polygon(u$bdry[[i]]$x / xdim, 
                  u$bdry[[i]]$y / ydim, border = locator_color)
        }
      }
    }
    
    # reset graphical parameters when function exits:
    current_par <- graphics::par(no.readonly = TRUE)
    on.exit(graphics::par(current_par))
    
    # set layout
    graphics::layout(matrix(1:3, nrow = 1),
                     widths = rep(1, 3))
    
    # plot original image
    graphics::par(mar = c(0, 0, 2, 0))
    recolorize::plotImageArray(rc_obj$original_img,
                               main = "Recolored original")
    plot_region()
    
    # plot old zone map with polygon/rectangle
    graphics::par(mar = c(0, 0, 2, 0))
    recolorize::plotImageArray(constructImage(rc_original_pix, rc_obj$centers),
                               main = "Input")
    plot_region()
    
    # plot new color map & palette
    graphics::par(mar = c(0, 0, 2, 0))
    recolorize::plotImageArray(recoloredImage(rc_obj),
                               main = "Output")
    plot_region()
  }
  return(rc_obj)
}
```

#Cleaning manually holes in wings
```{r, include=FALSE, echo=FALSE}
#for forewings
for (i in c(2, 5, 6, 8, 10, 18)){
  if (i %in% c(2, 5, 18)){
    rc_obj <- impose_list[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 4, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = FALSE)
    impose_list[[i]] <- rc_obj_2
  }
  if (i %in% c(5,6)){
    rc_obj <- impose_list[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 3, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = TRUE)
    impose_list[[i]] <- rc_obj_2
  }
  if (i %in% c(8, 10)){
    rc_obj <- impose_list[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 1, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = TRUE)
    impose_list[[i]] <- rc_obj_2
  }
}

#for hindwings
for (i in c(1, 4, 7, 9, 10, 11, 13, 17, 18, 19, 20, 22, 23, 24, 29, 30)){
  if (i %in% c(7,10,18,23)){
    rc_obj <- impose_list_hind[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 1, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = TRUE)
    impose_list_hind[[i]] <- rc_obj_2
  }
  if (i %in% c(1,4,9,11,13,19,20,22,24,29,30)){
    rc_obj <- impose_list_hind[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 2, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = TRUE)
    impose_list_hind[[i]] <- rc_obj_2
  }
  if (i %in% c(17)){
    rc_obj <- impose_list_hind[[i]]
    rc_obj_2 <- recolor_selection(rc_obj, color_to = 3, 
                              selection = "polygon", 
                              locator_color = "yellow", 
                              n_polygons = 1, plotting = TRUE, recolor_background = TRUE)
    impose_list_hind[[i]] <- rc_obj_2
  }
}
```

#Cleaning small dots of the wrong color in the middle of another color
```{r, include=FALSE, echo=FALSE}
# make an empty list for storing the recolorize objects
absorbed_list <- impose_list

for (i in 1:length(impose_list)) {
  for (j in 1:2){
    absorbed_list[[i]] <- absorbLayer(absorbed_list[[i]],
                                      layer_idx = j,
                                      size_condition = function(s) s<70,
                                      plotting = FALSE)
  }
  absorbed_list[[i]] <- absorbLayer(absorbed_list[[i]],
                                      layer_idx = 3,
                                      size_condition = function(s) s<50,
                                      plotting = FALSE)
}

# make an empty list for storing the recolorize objects
absorbed_list_hind <- impose_list_hind

for (i in 1:length(impose_list_hind)) {
  for (j in 1:2){
    absorbed_list_hind[[i]] <- absorbLayer(absorbed_list_hind[[i]],
                                      layer_idx = j,
                                      size_condition = function(s) s<70,
                                      plotting = FALSE)
  }
  absorbed_list_hind[[i]] <- absorbLayer(absorbed_list_hind[[i]],
                                      layer_idx = 3,
                                      size_condition = function(s) s<20,
                                      plotting = FALSE)
}


for (i in 1:length(absorbed_list_hind)) {
  plot(absorbed_list_hind[[i]])
}

```

#Merging my blue layers ofr the forewings
```{r, include=FALSE, echo=FALSE}
# make an empty list for storing the recolorize objects
final_list <- absorbed_list

for (i in 1:length(final_list)){
  final_list[[i]] <- mergeLayers(final_list[[i]], merge_list = c(1, 2), plotting = FALSE, color_to = morpho_palette2[2,])
  plot(final_list[[i]])
}
```

#Saving the cleaned recolorize images as patternize and the original image for plotting on the PCA later on
```{r, include=FALSE, echo=FALSE}
# convert to patternize:
patternize_list <- lapply(final_list, recolorize_to_patternize)

# save RDS file
saveRDS(patternize_list, "rds_file/processed_images.rds")

or_list <- vector("list", length(final_list))
names(or_list) <- names(final_list)
for (i in 1:length(final_list)){
  or_list[[i]] <- final_list[[i]]$original_img
}
saveRDS(or_list, "rds_file/or_images.rds")


# convert to patternize:
patternize_list_hind <- lapply(absorbed_list_hind, recolorize_to_patternize)

# save RDS file
saveRDS(patternize_list_hind, "rds_file/processed_images_hind.rds")

or_list_hind <- vector("list", length(absorbed_list_hind))
names(or_list_hind) <- names(absorbed_list_hind)
for (i in 1:length(absorbed_list_hind)){
  or_list_hind[[i]] <- absorbed_list_hind[[i]]$original_img
}
saveRDS(or_list_hind, "rds_file/or_images_hind.rds")
```

#Creating patPCA function (bc I can't seem to import it...)
```{r}
#' Run a PCA on multiple colors
#' 
#' Runs a PCA on two or more colors from a patternize raster list.
#' 
#' @param rList List of raster objects, where each element is an individual, and
#'   the list elements of that element are individual color pattern layers for
#'   that individual.
#' @param which_colors Either "all" (the default) or a numeric vector indicating
#'   which colors to use for the combined PCA.
#' @param PCx,PCy Which principal components to plot on the X and Y axes, if
#'   plotting.
#' @param plotting Logical. Plot PCA results?
#' @param quietly Logical. Print progress messages?
#' 
#' @return A [stats::prcomp] object for the specified colors.
#' 
#' @export
patPCA_total <- function(rList, which_colors = "all",
                         PCx = 1, PCy = 2,
                         plotting = TRUE, 
                         quietly = TRUE) {
  
  # determine the number of colors
  n_layers <- length(rList[[1]])
  IDlist <- names(rList)
  
  # restructure the raster list by layer instead of image
  rList <- lapply(1:n_layers,
                  function(i) lapply(rList,
                                     function(j) j[[i]]))
  
  # redefine to only specified layers (if not "all")
  if (sum(which_colors != "all") > 0) {
    if (!is.numeric(which_colors)) {
      stop("'which_colors' must be 'all' or a numeric vector indicating which
           colors should be used for the summed PCA")
    }
    rList <- rList[which_colors]
    n_layers <- length(which_colors)
  }
  
  
  if (!quietly) { message("Summing raster lists...") }
  
  # sum rasters after masking
  summedRasters <- lapply(rList,
                          function(i) patternize::sumRaster(i, IDlist, type = "RGB"))
  
  if (!quietly) { message("Making dataframe from rasters...") }
  
  # make a list for storing the raster dataframes
  rasDFlist <- vector("list", length = n_layers)
  
  # make one dataframe per layer
  for (l in 1:n_layers) {
    for (r in 1:length(rList[[1]])) {
      
      # isolate layer from image
      layer <- rList[[l]][[r]]
      
      # swap out NA values
      layer[is.na(layer)] <- 0
      
      # convert to a dataframe
      ras <- raster::as.data.frame(layer)
      
      # either start or append the dataframe for this layer
      if (r == 1) { rasDF <- ras } else { rasDF <- cbind(rasDF, ras) }
    }
    
    # set column names and add to the list
    colnames(rasDF) <- names(rList[[l]])
    rasDFlist[[l]] <- rasDF
  }
  
  # make a stacked version for the full PCA
  rasDFstack <- do.call(rbind, rasDFlist)
  
  if (!quietly) { message(paste("Running PCA on", n_layers, 
                                "colors and", ncol(rasDFstack), "images...")) }
  
  # run a PCA
  comp <- prcomp(t(rasDFstack))
  pcdata <- comp$x
  rotation <- comp$rotation
  summ <- summary(comp)
  
  if (!quietly) { message("done") }
  
  if (plotting) {
    xrange <- range(pcdata[ , PCx])
    yrange <- range(pcdata[ , PCy])
    
    # be polite
    current_par <- par(no.readonly = TRUE)
    on.exit(par(current_par))
    
    # set parameters and plot
    par(mfrow=c(1,1), mar=c(4,4,2,2))
    plot(comp$x[,c(PCx,PCy)], col='black', pch=19,
         xlim = xrange, ylim = yrange,
         xlab=paste0('PC',PCx,' (', round(summ$importance[2,PCx]*100, 1), ' %)'),
         ylab=paste0('PC',PCy,' (', round(summ$importance[2,PCy]*100, 1), ' %)'))
    
  }
  
  # return the pca:
  return(comp)
  
}
```

#Patternize analysis of the images
```{r, include=FALSE, echo=FALSE}
#loading images
patternize_list <- readRDS("rds_file/processed_images.rds")

# and set extents again:
for (i in 1:length(patternize_list)) {
  for (j in 1:length(patternize_list[[1]])) {
    raster::extent(patternize_list[[i]][[j]]) <- extent_list[[i]]
  }
}

#NOW for forewings we merge the layer 3 and 4 which were useful 
# Function to merge Layer 3 and Layer 4, then remove Layer 4
merge_layers <- function(raster_list) {
  raster_list[[3]] <- raster::overlay(raster_list[[3]], raster_list[[4]], fun = function(x, y) ifelse(x == 1 | y == 1, 1, 0))
  raster_list <- raster_list[1:3]  # Remove Layer 4
  return(raster_list)
}
# Apply function to each element of patternize_list
patternize_list <- lapply(patternize_list, merge_layers)

morpho_pca <- patPCA_total(patternize_list, quietly = FALSE)
summary(morpho_pca) #we keep 17 axis
test_data <- as.data.frame(morpho_pca$x)
test_data$ind <- str_sub(rownames(test_data), 1, 8)
zygo_df <- read.table("../../Documents/CollgeFr/Stage/Zygosity.txt", header=TRUE)
test_data <- full_join(test_data, zygo_df, by=join_by(ind==ind))
# sort out the individual location and color
# color
col <- rep(NA, length(test_data$Bioinformatic.name))
col[grep("blue", test_data$Bioinformatic.name)] <- "blue"
col[grep("oran", test_data$Bioinformatic.name)] <- "orange"
# location
loc <- rep(NA, length(test_data$Bioinformatic.name))
loc[grep("CAC", test_data$Bioinformatic.name)] <- "Cacao"
loc[grep("KAW", test_data$Bioinformatic.name)] <- "Kaw"
loc[grep("PAT", test_data$Bioinformatic.name)] <- "Patawa"
# remake data.frame
pca <- as_tibble(data.frame(test_data, col, loc))
#tests
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17) ~ col, pca)
Manova(model, test.statistic = "Pillai")
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17) ~ Zygosity, pca)
Manova(model, test.statistic = "Pillai")

# plot pca
b <- ggplot(pca, aes(PC1, PC2, col = Zygosity)) + 
  geom_point(size = 3) +
  scale_colour_manual(name="Genotype", labels=c("B/B", "B/O", "O/O"), limits=c("HOM_BL","HET","HOM_OR"), values = c("deepskyblue2", "goldenrod", "darkorange2"),) +
  xlab(paste0('PC1 (', round(summary(morpho_pca)$importance[2,1]*100, 1), ' %)')) +
  ylab(paste0('PC2 (', round(summary(morpho_pca)$importance[2,2]*100, 1), ' %)')) +
  coord_equal() +
  theme_classic()

#loading images
patternize_list_hind <- readRDS("rds_file/processed_images_hind.rds")

# and set extents again:
for (i in 1:length(patternize_list_hind)) {
  for (j in 1:length(patternize_list_hind[[1]])) {
    raster::extent(patternize_list_hind[[i]][[j]]) <- extent_list_hind[[i]]
  }
}

#source("patPCA_total.R")
morpho_pca_hind <- patPCA_total(patternize_list_hind, quietly = FALSE)
summary(morpho_pca_hind) #we keep 22 axis
test_data <- as.data.frame(morpho_pca_hind$x)
test_data$ind <- str_sub(rownames(test_data), 1, 8)
test_data <- full_join(test_data, zygo_df, by=join_by(ind==ind))
# sort out the individual location and color
# color
col <- rep(NA, length(test_data$Bioinformatic.name))
col[grep("blue", test_data$Bioinformatic.name)] <- "blue"
col[grep("oran", test_data$Bioinformatic.name)] <- "orange"
# location
loc <- rep(NA, length(test_data$Bioinformatic.name))
loc[grep("CAC", test_data$Bioinformatic.name)] <- "Cacao"
loc[grep("KAW", test_data$Bioinformatic.name)] <- "Kaw"
loc[grep("PAT", test_data$Bioinformatic.name)] <- "Patawa"
# remake data.frame
pca <- as_tibble(data.frame(test_data, col, loc))
#tests
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17, PC18, PC19, PC20, PC21, PC22) ~ col, pca)
Manova(model, test.statistic = "Pillai")
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17, PC18, PC19, PC20, PC21, PC22) ~ Zygosity, pca)
Manova(model, test.statistic = "Pillai")

# plot pca
c <- ggplot(pca, aes(PC1, PC2, col = Zygosity)) + 
  geom_point(size = 3) +
  scale_colour_manual(name="Genotype", labels=c("B/B", "B/O", "O/O"), limits=c("HOM_BL","HET","HOM_OR"), values = c("deepskyblue2", "goldenrod", "darkorange2"),) +
  xlab(paste0('PC1 (', round(summary(morpho_pca_hind)$importance[2,1]*100, 1), ' %)')) +
  ylab(paste0('PC2 (', round(summary(morpho_pca_hind)$importance[2,2]*100, 1), ' %)')) +
  coord_equal() +
  theme_classic()
```

#Plot with wings pattern
```{r}
library(ggplot2)
library(gridGraphics)
library(grid)
library(gridExtra)

plot_base <- function(){
  #first, make a blank plot
  PCx <- 1; PCy <- 2
  pca_summary <- summary(morpho_pca)
  limits <- apply(morpho_pca$x[ , c(PCx, PCy)], 2, range)
  par(mar = c(4, 4, 2, 1), mgp=c(2, 0.3, 0))
  plot(morpho_pca$x[ , c(PCx, PCy)], type = "n",
       asp = 1,
       xlim = limits[ , 1] + c(-20, 10), 
       ylim = limits[ , 2] + c(-10, 10),
       bty = "l",
       cex.axis=0.9,
       las=1,
       tck=-0.003,
       xlab=paste0('PC1 (', round(pca_summary$importance[2, PCx]*100, 1), ' %)'),
       ylab=paste0('PC2 (', round(pca_summary$importance[2, PCy]*100, 1), ' %)'))
  
  #load images
  original_list <- readRDS("rds_file/or_images.rds")
  
  # then add images:
  for (i in 1:length(original_list)) {
    recolorize::add_image(original_list[[i]], 
              x = morpho_pca$x[i, PCx]+10,
              y = morpho_pca$x[i, PCy]+20,
              width = 20, angle=180)
  }
}

plot_base()
grid.newpage()
grid.echo(plot_base())
g1 <- grid.grab()

# Afficher cte  cte
ggarrange(g1, b, labels = c("A", "B"), widths = c(1,1))

plot_base <- function(){
  # first, make a blank plot
  PCx <- 1; PCy <- 2
  pca_summary <- summary(morpho_pca_hind)
  limits <- apply(morpho_pca_hind$x[ , c(PCx, PCy)], 2, range)
  par(mar = c(4, 4, 2, 1), mgp=c(2, 0.3, 0))
  plot(morpho_pca_hind$x[ , c(PCx, PCy)], type = "n",
       asp = 1,
       bty = "l",
       cex.axis=0.9,
       las=1,
       tck=-0.004,
       xlim = limits[ , 1] + c(15, 0),
       ylim = limits[ , 2] + c(0, 10),
       xlab=paste0('PC1 (', round(pca_summary$importance[2, PCx]*100, 1), ' %)'),
       ylab=paste0('PC2 (', round(pca_summary$importance[2, PCy]*100, 1), ' %)'))
  
  #load images
  original_list <- readRDS("rds_file/or_images_hind.rds")
  
  # then add images:
  for (i in 1:length(original_list)) {
    recolorize::add_image(original_list[[i]], 
              x = morpho_pca_hind$x[i, PCx]+20,
              y = morpho_pca_hind$x[i, PCy]+20,
              width = 15, angle=180)
  }
}
plot_base()
grid.newpage()
grid.echo(plot_base())
g2 <- grid.grab()

# Afficher cte  cte
ggarrange(g2, c, labels = c("A", "B"), widths = c(1,1))
```

##let's merge my raster of fore and hind wings
```{r}
patPCA_wings <- function(rList1, rList2, LayerOrder, which_colors = "all",
                         PCx = 1, PCy = 2,
                         plotting = TRUE, 
                         quietly = TRUE) {
  
  # determine the number of colors
  n_layers <- length(rList1[[1]])
  IDlist <- names(rList1)
  
  # restructure the raster list by layer instead of image
  rList1 <- lapply(1:n_layers,
                  function(i) lapply(rList1,
                                     function(j) j[[i]]))
  rList2 <- lapply(1:n_layers,
                  function(i) lapply(rList2,
                                     function(j) j[[i]]))
  
  if (!quietly) { message("Reordering layers...") }
  
  #reorder the layers accordingly
  if (any(LayerOrder!=1:length(LayerOrder))){
    rList2[1:length(rList2)] <- rList2[LayerOrder]
  }
  
  # redefine to only specified layers (if not "all")
  if (sum(which_colors != "all") > 0) {
    if (!is.numeric(which_colors)) {
      stop("'which_colors' must be 'all' or a numeric vector indicating which
           colors should be used for the summed PCA")
    }
    rList1 <- rList1[which_colors]
    n_layers <- length(which_colors)
  }
  
  if (!quietly) { message("Summing raster lists...") }
  
  # sum rasters after masking
  summedRasters <- lapply(rList1,
                          function(i) patternize::sumRaster(i, IDlist, type = "RGB"))
  
  if (!quietly) { message("Making dataframe from rasters...") }
  
  # make a list for storing the raster dataframes
  rasDFlist <- vector("list", length = n_layers)
  
  # make one dataframe per layer
  for (l in 1:n_layers) {
    for (r in 1:length(rList1[[1]])) {
      
      # isolate layer from image
      layer1 <- rList1[[l]][[r]]
      layer2 <- rList2[[l]][[r]]
      
      # swap out NA values
      layer1[is.na(layer1)] <- 0
      layer2[is.na(layer2)] <- 0
      
      # convert to a dataframe
      ras1 <- raster::as.data.frame(layer1)
      ras2 <- raster::as.data.frame(layer2)
      
      #combine layers
      ras <- rbind(ras1, ras2)
      
      # either start or append the dataframe for this layer
      if (r == 1) { rasDF <- ras } else { rasDF <- cbind(rasDF, ras) }
    }
    
    # set column names and add to the list
    colnames(rasDF) <- names(rList1[[l]])
    rasDFlist[[l]] <- rasDF
  }
  
  # make a stacked version for the full PCA
  rasDFstack <- do.call(rbind, rasDFlist)
  
  if (!quietly) { message(paste("Running PCA on", n_layers, 
                                "colors and", ncol(rasDFstack), "images...")) }
  
  # run a PCA
  comp <- prcomp(t(rasDFstack))
  pcdata <- comp$x
  rotation <- comp$rotation
  summ <- summary(comp)
  
  if (!quietly) { message("done") }
  
  if (plotting) {
    xrange <- range(pcdata[ , PCx])
    yrange <- range(pcdata[ , PCy])
    
    # be polite
    current_par <- par(no.readonly = TRUE)
    on.exit(par(current_par))
    
    # set parameters and plot
    par(mfrow=c(1,1), mar=c(4,4,2,2))
    plot(comp$x[,c(PCx,PCy)], col='black', pch=19,
         xlim = xrange, ylim = yrange,
         xlab=paste0('PC',PCx,' (', round(summ$importance[2,PCx]*100, 1), ' %)'),
         ylab=paste0('PC',PCy,' (', round(summ$importance[2,PCy]*100, 1), ' %)'))
    
  }
  
  # return the pca:
  return(comp)
  
}

morpho_pca_wings <- patPCA_wings(patternize_list, patternize_list_hind, c(2, 3, 1), quietly = FALSE)
summary(morpho_pca_wings)#we keep 21 axis
test_data <- as.data.frame(morpho_pca_wings$x)
test_data$ind <- str_sub(rownames(test_data), 1, 8)
test_data <- full_join(test_data, zygo_df, by=join_by(ind==ind))
# sort out the individual location and color
# color
col <- rep(NA, length(test_data$Bioinformatic.name))
col[grep("blue", test_data$Bioinformatic.name)] <- "blue"
col[grep("oran", test_data$Bioinformatic.name)] <- "orange"
# location
loc <- rep(NA, length(test_data$Bioinformatic.name))
loc[grep("CAC", test_data$Bioinformatic.name)] <- "Cacao"
loc[grep("KAW", test_data$Bioinformatic.name)] <- "Kaw"
loc[grep("PAT", test_data$Bioinformatic.name)] <- "Patawa"
# remake data.frame
pca <- as_tibble(data.frame(test_data, col, loc))
#tests
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17, PC18, PC19, PC20, PC21) ~ col, pca)
Manova(model, test.statistic = "Pillai")
model <- lm(cbind(PC1, PC2, PC3, PC4, PC5, PC6, PC7, PC8, PC9, PC10, PC11, PC12, PC13, PC14, PC15, PC16, PC17, PC18, PC19, PC20, PC21) ~ Zygosity, pca)
Manova(model, test.statistic = "Pillai")

#asses variation among group
scores <- as.data.frame(morpho_pca_wings$x[, 1:2])
scores$group <- pca$col
get_ellipse_area <- function(df) {
  cov_matrix <- cov(df[, 1:2])
  eig_vals <- eigen(cov_matrix)$values
  pi * sqrt(eig_vals[1]) * sqrt(eig_vals[2])
}
areas <- scores %>%
  group_by(group) %>%
  group_split() %>%
  setNames(unique(pca$col)) %>%
  lapply(get_ellipse_area)
print(areas[[1]]/(areas[[2]]+areas[[1]]))

# plot pca
d <- ggplot(pca, aes(PC1, PC2, col = Zygosity)) + 
  geom_point(size = 3) +
  scale_colour_manual(name="Genotype", labels=c("B/B", "B/O", "O/O"), limits=c("HOM_BL","HET","HOM_OR"), values = c("deepskyblue2", "goldenrod", "darkorange2"),) +
  xlab(paste0('PC1 (', round(summary(morpho_pca_wings)$importance[2,1]*100, 1), ' %)')) +
  ylab(paste0('PC2 (', round(summary(morpho_pca_wings)$importance[2,2]*100, 1), ' %)')) +
  coord_equal() +
  theme_classic()

plot_base <- function(){
  # first, make a blank plot
  PCx <- 1; PCy <- 2
  pca_summary <- summary(morpho_pca_wings)
  limits <- apply(morpho_pca_wings$x[ , c(PCx, PCy)], 2, range)
  par(mar = c(4, 4, 2, 1), mgp=c(2, 0.3, 0))
  plot(morpho_pca_wings$x[ , c(PCx, PCy)], type = "n",
       asp = 1,
       bty = "l",
       cex.axis=0.9,
       las=1,
       tck=-0.003,
       xlim = limits[ , 1] + c(0, 5), 
       ylim = limits[ , 2] + c(-20, 10),
       xlab=paste0('PC1 (', round(pca_summary$importance[2, PCx]*100, 1), ' %)'),
       ylab=paste0('PC2 (', round(pca_summary$importance[2, PCy]*100, 1), ' %)'))
  
  #load images
  original_fore <- readRDS("rds_file/or_images.rds")
  original_hind <- readRDS("rds_file/or_images_hind.rds")
  
  # then add images:
  for (i in 1:length(original_fore)) {
    recolorize::add_image(original_fore[[i]], 
              x = morpho_pca_wings$x[i, PCx]+20,
              y = morpho_pca_wings$x[i, PCy]+15,
              width = 15, angle=180)
    recolorize::add_image(original_hind[[i]], 
              x = morpho_pca_wings$x[i, PCx]+20,
              y = morpho_pca_wings$x[i, PCy],
              width = 15, angle=180)
  }
}
plot_base()
grid.newpage()
grid.echo(plot_base())
g3 <- grid.grab()

# Afficher cte  cte
ggarrange(g3, d, labels = c("A", "B"), widths = c(1,1))
```

##let's merge my raster of fore and hind wings
```{r}
createPhenotype(morpho_pca, c(0,40), IDlist, rasterList = imageList_aligned, cartoonID = ('FG24.087_D'))
```